Chapter 2 Draft

### 2020-05-26 Rmd/Quantitative_Data_Models_plot.Rmd
Models part 5

corolla_length_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

@@

>>>>

corolla_length_2 <- ggplot(mydf, aes(x = x, y = predicted)) + theme_ds4psy() + theme(legend.position = "none") + xlab("Corolla length (mm)")+ ylab("Predicted d")+geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

@@

model_4 <- readRDS("Data/RData/model_4_visits_plant_height_4.rds")
pred <- readRDS("Data/RData/pred_plot_visits_plant_height_4.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_plant_height_4.rds")

mydf <- ggpredict(model_4, terms = c("plant_height_mean_m"))
plant_height_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Plant height") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_4 <- readRDS("Data/RData/model_4_visits_style_length_4.rds")
pred <- readRDS("Data/RData/pred_plot_visits_style_length_4.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_style_length_4.rds")

mydf <- ggpredict(model_4, terms = c("style_length_mm"))
style_length_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Style length (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_4 <- readRDS("Data/RData/model_4_visits_corolla_length_4.rds")
pred <- readRDS("Data/RData/pred_plot_visits_corolla_length_4.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_length_4.rds")

mydf <- ggpredict(model_4, terms = c("Corolla_length_mean"))
corolla_length_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Corolla length (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =Corolla_length_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_4 <- readRDS("Data/RData/model_4_visits_corolla_diameter_4.rds")
pred <- readRDS("Data/RData/pred_plot_visits_corolla_diameter_4.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_corolla_diameter_4.rds")

mydf <- ggpredict(model_4, terms = c("Corolla_diameter_mean"))
corolla_diameter_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Corolla diameter (mm)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =Corolla_diameter_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_4 <- readRDS("Data/RData/model_4_visits_ovule_number_4.rds")
pred <- readRDS("Data/RData/pred_plot_visits_ovule_number_4.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_ovule_number_4.rds")

mydf <- ggpredict(model_4, terms = c("ovules_mean"))
ovule_number_4 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Ovule number") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted normalise degree") +geom_point(data= all_tf, aes(x =ovules_mean , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

p <- plot_grid(plant_height_4,style_length_4, corolla_length_4,corolla_diameter_4,ovule_number_4,NULL, ncol = 2)

title <- ggdraw() + draw_label("Normalise degree ~ TRAITS", fontface='bold')
